R, Python, and Ruby clients for GBIF species occurrence data

### 2020-02-27 manuscript_mee.tex
tweaks to mee paper

\documentclass[author-year, review, 11pt]{components/elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}
\usepackage{lineno} % add
  \linenumbers % turns line numbering on
\bibliographystyle{elsarticle-harv}
\biboptions{sort&compress} % For natbib
\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%% Redefines the elsarticle footer
\makeatletter
\def\ps@pprintTitle{%
 \let\@oddhead\@empty
 \let\@evenhead\@empty
 \def\@oddfoot{\it \hfill\today}%
 \let\@evenfoot\@oddfoot}
 \def\tightlist{}
\makeatother

% A modified page layout
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in
%%%%%%%%%%%%%%%% end my additions to header

@@

@@

            pdftitle={R Python, and Ruby clients for GBIF species occurrence data},
            colorlinks=true,

@@

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}

@@

@@

  \title{R Python, and Ruby clients for GBIF species occurrence data}
    \author[cstar]{Scott Chamberlain\corref{c1}}
   \ead{scott(at)ropensci.org} 
   \cortext[c1]{Corresponding author}
    \author[boettig]{Carl Boettiger}
   \ead{carl(at)ropensci.org}

      \address[cstar]{rOpenSci, Museum of Paleontology, University of California, Berkeley,
CA, USA}
    \address[boettig]{rOpenSci, Department of Enivornmental Science, Policy and Management,
University of California, Berkeley, CA, USA}

@@

  Email address:
  \href{mailto:scott@ropensci.org}{\nolinkurl{scott@ropensci.org}}

@@

\section{Introduction}\label{introduction}

Perhaps the most fundamental element in many fields of ecology is the
individual organism. The number of individuals of each species in a
given location forms the basis for many sub-fields of ecology and
evolution. Some research questions necessitate collecting new data,
while others can easily take advantage of existing data. In fact, some
ecology fields are built largely on existing data, e.g., macro-ecology
(Brown, 1995; Beck et al., 2012).

Data on individuals, including which species, and where they're found,
can be used for a large number of research questions. Biodiversity
records have been used for a suite of other use cases: validating
habitat suitability models with real occurrence data (Ficetola et al.,
2014); ancestral range reconstruction (Ferretti et al., 2015; María
Mendoza et al., 2015); development of invasive species watch lists
(Faulkner et al., 2014); evaluating risk of invasive species spread
(Febbraro et al., 2013); and effects of climate change on future
biodiversity (Brown et al., 2015).

In addition to wide utility, this data is important for conservation.
Biodiversity loss is one of the greatest challenges of our time (Pimm et
al., 2014), and some have called this the sixth great mass extinction
(Ceballos et al., 2015). Given this challenge there is a great need for
data on specimen records, whether collected from live sightings in the
field or specimens in museums.

\section{Global Biodiversity Information
Facility}\label{global-biodiversity-information-facility}

@@

\section{The clients}\label{the-clients}

@@

\subsection{rgbif}\label{rgbif}

Herein, we describe the \texttt{rgbif} software package (Chamberlain et
al.) for working with GBIF data in the R programming environment (R Core
Team, 2014). R is a widely used language in academia, as well as
non-profit and private sectors. Importantly, R makes it easy to execute
all steps of the research process, including data management, data
manipulation and cleaning, statistics, and visualization. Thus, an R
client for getting GBIF data is a powerful tool to facilitate
reproducible research.

The \texttt{rgbif} package is nearly completely written in R (a small
Javascript library is included for reading well known text (Herring,
2011)), uses an \href{http://choosealicense.com/licenses/mit/}{MIT
license} to maximize use everywhere. \texttt{rgbif} is developed
publicly on GitHub at \url{https://github.com/ropensci/rgbif}, where
development versions of the package can be installed, and bugs and
feature requests reported. Stable versions of \texttt{rgbif} can be
installed from
\href{https://cran.rstudio.com/web/packages/rgbif/}{CRAN}, the
distribution network for R packages. \texttt{rgbif} is part of the
rOpenSci project (\url{http://ropensci.org}), a developer network making
R software to facilitate reproducible research.

\subsection{pygbif}\label{pygbif}

@@

The \texttt{pygbif} library is less mature and complete than the R
package. It also uses an
\href{http://choosealicense.com/licenses/mit/}{MIT license} to maximize
use everywhere. \texttt{pygbif} is developed publicly on GitHub at
\url{https://github.com/sckott/pygbif}, where development versions of
the package can be installed, and bugs and feature requests reported.
Stable versions of \texttt{pygbif} can be installed from
\href{https://pypi.python.org/pypi/pygbif}{pypi}, the distribution
network for Python libraries.

\subsection{gbifrb}\label{gbifrb}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{require }\StringTok{'gbifrb'}
\end{Highlighting}
\end{Shaded}

The \texttt{gbifrb} library is less mature and complete than the R and
Python libraries. It also uses an
\href{http://choosealicense.com/licenses/mit/}{MIT license} to maximize
use everywhere. \texttt{gbifrb} is developed publicly on GitHub at
\url{https://github.com/sckott/gbifrb}, where development versions of
the package can be installed, and bugs and feature requests reported.
Stable versions of \texttt{gbifrb} can be installed from
{[}Rubygems{]}{[}gemgbif{]}, the distribution network for Ruby
libraries.

\subsubsection{Library interfaces}\label{library-interfaces}

\texttt{rgbif}, \texttt{pygbif}, and \texttt{gbifrb} are designed
following the \href{http://www.gbif.org/developer/summary}{GBIF
Application Programming Interface}, or API. The GBIF API has four major
components: registry, taxonomic names, occurrences, and maps. We also
include functions to interface with the OAI-PMH GBIF service; only
dataset (registry) information is available via this service, however.
An interface to the GBIF maps API is in development for \texttt{rgbif},
but is non-existent for both \texttt{pygbif} and \texttt{gbifrb}. All
three libraries have a suite of functions dealing with each of registry,
taxonomic, names, and occurrences - we'll go through each in turn
describing design of the user interface and example usage.

\subsection{GBIF headers}\label{gbif-headers}

@@

\subsection{Registry}\label{registry}

@@

\subsubsection{Datasets}\label{datasets}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res <-}\StringTok{ }\KeywordTok{dataset_search}\NormalTok{(}\DataTypeTok{query =} \StringTok{"oregon"}\NormalTok{)}
\NormalTok{res}\OperatorTok{$}\NormalTok{data}\OperatorTok{$}\NormalTok{datasetTitle[}\DecValTok{1}\OperatorTok{:}\DecValTok{10}\NormalTok{]}
\CommentTok{#>  [1] "Oregon State Ichthyology Collection"                                                                                                                                                  }
\CommentTok{#>  [2] "Oregon State University Herpetological Collection"                                                                                                                                    }
\CommentTok{#>  [3] "Mygalomorph spiders from southwestern Oregon, USA, with descriptions of four new species"                                                                                             }
\CommentTok{#>  [4] "A new species of Helobdella (Hirudinida: Glossiphoniidae) from Oregon, USA"                                                                                                           }
\CommentTok{#>  [5] "Annotated Checklist of the large branchiopod crustaceans of Idaho, Oregon and Washington, USA, with the “ rediscovery ” of a new species of Branchinecta (Anostraca: Branchinectidae)"}
\CommentTok{#>  [6] "A new species of Chrysobothris Eschscholtz from Oregon and Washington, with notes on other Buprestidae (Coleoptera) occurring in the United States and Canada"                        }
\CommentTok{#>  [7] "Three new species of Grylloblatta Walker (Insecta: Grylloblattodea: Grylloblattidae), from southern Oregon and northern California"                                                   }
\CommentTok{#>  [8] "A new species of Cladotanytarsus (Lenziella) from Oregon supports the systematic concept of the subgenus (Diptera: Chironomidae)"                                                     }
\CommentTok{#>  [9] "A new monster from southwest Oregon forests: Cryptomasterbehemoth sp. n. (Opiliones, Laniatores, Travunioidea)"                                                                       }
\CommentTok{#> [10] "Two new species of Fluminicola (Caenogastropoda, Lithoglyphidae) from southwest Oregon, USA, and a range extension for F. multifarius"}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{require }\StringTok{'gbifrb'}
\NormalTok{registry = }\DataTypeTok{Gbif}\NormalTok{::}\DataTypeTok{Registry}
\NormalTok{registry.datasets(}\StringTok{type: "OCCURRENCE"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\paragraph{Dataset metrics}\label{dataset-metrics}

Dataset metrics are another useful way of figuring out what datasets you
may want to use. One drawback is that these metrics data are only
available for datasets of type \emph{checklist}, but there are quite a
lot of them (21697).

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res <-}\StringTok{ }\KeywordTok{dataset_metrics}\NormalTok{(}\DataTypeTok{uuid=}\StringTok{'ec93a739-1681-4b04-b62f-3a687127a17f'}\NormalTok{)}
\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{rank =} \KeywordTok{names}\NormalTok{(res}\OperatorTok{$}\NormalTok{countByRank),}
           \DataTypeTok{count =} \KeywordTok{unname}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(res}\OperatorTok{$}\NormalTok{countByRank)))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ pygbif }\ImportTok{import}\NormalTok{ registry}
\NormalTok{registry.dataset_metrics(uuid}\OperatorTok{=}\StringTok{'ec93a739-1681-4b04-b62f-3a687127a17f'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{require }\StringTok{'gbifrb'}
\NormalTok{registry = }\DataTypeTok{Gbif}\NormalTok{::}\DataTypeTok{Registry}
\NormalTok{registry.dataset_metrics(}\StringTok{uuid: 'ec93a739-1681-4b04-b62f-3a687127a17f'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\subsubsection{Networks, nodes, and
installations}\label{networks-nodes-and-installations}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{networks}\NormalTok{(}\DataTypeTok{limit =} \DecValTok{10}\NormalTok{)}\OperatorTok{$}\NormalTok{data}\OperatorTok{$}\NormalTok{title}
\CommentTok{#>  [1] "GBIF Backbone Sources"                                      }
\CommentTok{#>  [2] "Canadensys"                                                 }
\CommentTok{#>  [3] "Southwest Collections of Arthropods Network (SCAN)"         }
\CommentTok{#>  [4] "VertNet"                                                    }
\CommentTok{#>  [5] "Dryad"                                                      }
\CommentTok{#>  [6] "GBIF Network"                                               }
\CommentTok{#>  [7] "The Knowledge Network for Biocomplexity (KNB) "             }
\CommentTok{#>  [8] "Online Zoological Collections of Australian Museums (OZCAM)"}
\CommentTok{#>  [9] "Catalogue of Life"                                          }
\CommentTok{#> [10] "Ocean Biogeographic Information System (OBIS)"}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{require }\StringTok{'gbifrb'}
\NormalTok{registry = }\DataTypeTok{Gbif}\NormalTok{::}\DataTypeTok{Registry}
\NormalTok{registry.networks(}\StringTok{limit: }\DecValTok{10}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\subsection{Taxonomic names}\label{taxonomic-names}

@@

\subsubsection{GBIF Backbone}\label{gbif-backbone}

The GBIF backbone taxonomy is used in GBIF to have a consistent way to
refer to taxonomic names throughout their services. The backbone has
5869207 unique names and 2818534 species names. The backbone taxonomy is
also a dataset with key \texttt{d7dddbf4-2cf0-4f39-9b2a-bb099caae36c}
(\url{https://www.gbif.org/dataset/d7dddbf4-2cf0-4f39-9b2a-bb099caae36c}).

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res <-}\StringTok{ }\KeywordTok{name_backbone}\NormalTok{(}\DataTypeTok{name=}\StringTok{'Poa'}\NormalTok{, }\DataTypeTok{rank=}\StringTok{'genus'}\NormalTok{, }\DataTypeTok{family=}\StringTok{'Poaceae'}\NormalTok{)}
\NormalTok{res[}\KeywordTok{c}\NormalTok{(}\StringTok{'usageKey'}\NormalTok{, }\StringTok{'kingdom'}\NormalTok{)]}
\CommentTok{#> $usageKey}
\CommentTok{#> [1] 2704173}
\CommentTok{#> }
\CommentTok{#> $kingdom}
\CommentTok{#> [1] "Plantae"}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ pygbif }\ImportTok{import}\NormalTok{ species}
\NormalTok{res }\OperatorTok{=}\NormalTok{ species.name_backbone(name}\OperatorTok{=}\StringTok{'Poa'}\NormalTok{, rank}\OperatorTok{=}\StringTok{'genus'}\NormalTok{, family}\OperatorTok{=}\StringTok{'Poaceae'}\NormalTok{)}
\NormalTok{[ res[x] }\ControlFlowTok{for}\NormalTok{ x }\KeywordTok{in}\NormalTok{ [}\StringTok{'usageKey'}\NormalTok{, }\StringTok{'kingdom'}\NormalTok{] ]}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{require }\StringTok{'gbifrb'}
\NormalTok{species = }\DataTypeTok{Gbif}\NormalTok{::}\DataTypeTok{Species}
\NormalTok{res = species.name_backbone(}\StringTok{name: 'Poa'}\NormalTok{, }\StringTok{rank: 'genus'}\NormalTok{, }\StringTok{family: 'Poaceae'}\NormalTok{)}
\NormalTok{res.select \{ |k,v| k.match(}\OtherTok{/usageKey|kingdom/}\NormalTok{) \}}
\end{Highlighting}
\end{Shaded}

\subsubsection{Name searching}\label{name-searching}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{name_suggest}\NormalTok{(}\DataTypeTok{q=}\StringTok{'Pum'}\NormalTok{, }\DataTypeTok{limit =} \DecValTok{6}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}rll@{}}
\toprule
key & canonicalName & rank\tabularnewline
\midrule
\endhead
2142856 & Althepus pum & SPECIES\tabularnewline
8589398 & Pumiliopimoidae & FAMILY\tabularnewline
8783253 & Pumililema & GENUS\tabularnewline
4823360 & Pumiliopareia & GENUS\tabularnewline
4635949 & Pumilina & GENUS\tabularnewline
4648228 & Pumilopaurus & GENUS\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ pygbif }\ImportTok{import}\NormalTok{ species}
\NormalTok{species.name_suggest(q}\OperatorTok{=}\StringTok{'Pum'}\NormalTok{, limit }\OperatorTok{=} \DecValTok{6}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{require }\StringTok{'gbifrb'}
\NormalTok{species = }\DataTypeTok{Gbif}\NormalTok{::}\DataTypeTok{Species}
\NormalTok{species.name_suggest(}\StringTok{q: 'Pum'}\NormalTok{, }\StringTok{limit: }\DecValTok{6}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\subsection{Occurrences}\label{occurrences}

@@

\subsubsection{Download API}\label{download-api}

@@

Request data download given a query. Here, we search for the taxon key
\texttt{3119195}, which is the key for \emph{Helianthus annuus}
(\url{http://www.gbif.org/species/3119195}).

>>>>

\documentclass[3p]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%%%%%%%%%%%%%%%% end my additions to header

@@

\bibliographystyle{elsarticle-harv}

@@

            pdftitle={R, Python, and Ruby clients for GBIF species occurrence data},
            colorlinks=false,

@@

\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

@@

\journal{Methods in Ecology and Evolution}
\linenumbers
\usepackage{setspace}
\doublespacing

@@

  \title{R, Python, and Ruby clients for GBIF species occurrence data}
    \author[cstar]{Scott Chamberlain\corref{Corresponding author}}
   \ead{myrmecocystus(at)gmail.com} 
    \author[boettig]{Carl Boettiger}
   \ead{cboettig(at)berkeley.edu} 
      \address[cstar]{rOpenSci, Museum of Paleontology, University of
California, Berkeley, CA, USA}
    \address[boettig]{rOpenSci, Department of Enivornmental Science,
Policy and Management, University of California, Berkeley, CA, USA}

@@

  Email address:
  \href{mailto:myrmecocystus@gmail.com}{\nolinkurl{myrmecocystus@gmail.com}}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Perhaps the most fundamental element in many fields of ecology is the
individual organism. The number of individuals of each species in a
given location forms the basis for many sub-fields of ecology and
evolution. Some research questions necessitate collecting new data,
while others can easily take advantage of existing data. In fact, some
ecology fields are built largely on existing data, e.g., macro-ecology
(Brown 1995; Beck \emph{et al.} 2012).

Data on individuals, including which species, and where they're found,
can be used for a large number of research questions. Biodiversity
records have been used for a suite of other use cases: validating
habitat suitability models with real occurrence data (Ficetola \emph{et
al.} 2014); ancestral range reconstruction (Ferretti \emph{et al.} 2015;
Marı́a Mendoza \emph{et al.} 2015); development of invasive species watch
lists (Faulkner \emph{et al.} 2014); evaluating risk of invasive species
spread (Febbraro \emph{et al.} 2013); and effects of climate change on
future biodiversity (Brown \emph{et al.} 2015).

In addition to wide utility, this data is important for conservation.
Biodiversity loss is one of the greatest challenges of our time (Pimm
\emph{et al.} 2014), and some have called this the sixth great mass
extinction (Ceballos \emph{et al.} 2015). Given this challenge there is
a great need for data on specimen records, whether collected from live
sightings in the field or specimens in museums.

\hypertarget{global-biodiversity-information-facility}{%
\section{Global Biodiversity Information
Facility}\label{global-biodiversity-information-facility}}

@@

\hypertarget{the-clients}{%
\section{The clients}\label{the-clients}}

@@

\hypertarget{rgbif}{%
\subsection{rgbif}\label{rgbif}}

Herein, we describe the \texttt{rgbif} software package (Chamberlain
\emph{et al.}) for working with GBIF data in the R programming
environment (R Core Team 2014). R is a widely used language in academia,
as well as non-profit and private sectors. Importantly, R makes it easy
to execute all steps of the research process, including data management,
data manipulation and cleaning, statistics, and visualization. Thus, an
R client for getting GBIF data is a powerful tool to facilitate
reproducible research.

The \texttt{rgbif} package is nearly completely written in R (a small
Javascript library is included for reading well known text (Herring
2011)), uses an \href{https://choosealicense.com/licenses/mit/}{MIT
license} to maximize use everywhere. \texttt{rgbif} is developed
publicly on GitHub at \url{https://github.com/ropensci/rgbif}, where
development versions of the package can be installed, and bugs and
feature requests reported. Stable versions of \texttt{rgbif} can be
installed from
\href{https://cran.rstudio.com/web/packages/rgbif/}{CRAN}, the
distribution network for R packages. \texttt{rgbif} is part of the
rOpenSci project (https://ropensci.org), a developer network making R
software to facilitate reproducible research.

\hypertarget{pygbif}{%
\subsection{pygbif}\label{pygbif}}

@@

The \texttt{pygbif} library is less mature and complete than the R
package. It also uses an
\href{https://choosealicense.com/licenses/mit/}{MIT license} to maximize
use everywhere. \texttt{pygbif} is developed publicly on GitHub at
\url{https://github.com/sckott/pygbif}, where development versions of
the package can be installed, and bugs and feature requests reported.
Stable versions of \texttt{pygbif} can be installed from
\href{https://pypi.python.org/pypi/pygbif}{pypi}, the distribution
network for Python libraries.

\hypertarget{gbifrb}{%
\subsection{gbifrb}\label{gbifrb}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{require }\StringTok{\textquotesingle{}gbifrb\textquotesingle{}}
\end{Highlighting}
\end{Shaded}

The \texttt{gbifrb} library is less mature and complete than the R and
Python libraries. It also uses an
\href{https://choosealicense.com/licenses/mit/}{MIT license} to maximize
use everywhere. \texttt{gbifrb} is developed publicly on GitHub at
\url{https://github.com/sckott/gbifrb}, where development versions of
the package can be installed, and bugs and feature requests reported.
Stable versions of \texttt{gbifrb} can be installed from
\href{https://rubygems.org/gems/gbifrb}{Rubygems}, the distribution
network for Ruby libraries.

\hypertarget{library-interfaces}{%
\section{Library interfaces}\label{library-interfaces}}

\texttt{rgbif}, \texttt{pygbif}, and \texttt{gbifrb} are designed
following the \href{https://www.gbif.org/developer/summary}{GBIF
Application Programming Interface}, or API. The GBIF API has four major
components: registry, taxonomic names, occurrences, and maps. We also
include functions to interface with the OAI-PMH GBIF service; only
dataset (registry) information is available via this service, however.
An interface to the GBIF maps API is in development for \texttt{rgbif},
but is non-existent for both \texttt{pygbif} and \texttt{gbifrb}. All
three libraries have a suite of functions dealing with each of registry,
taxonomic, names, and occurrences - we'll go through each in turn
describing design of the user interface and example usage.

\hypertarget{gbif-headers}{%
\subsection{GBIF headers}\label{gbif-headers}}

@@

\hypertarget{registry}{%
\subsection{Registry}\label{registry}}

@@

\hypertarget{datasets}{%
\subsection{Datasets}\label{datasets}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res <{-}}\StringTok{ }\KeywordTok{dataset\_search}\NormalTok{(}\DataTypeTok{query =} \StringTok{"oregon"}\NormalTok{)}
\NormalTok{res}\OperatorTok{$}\NormalTok{data}\OperatorTok{$}\NormalTok{datasetTitle[}\DecValTok{1}\OperatorTok{:}\DecValTok{10}\NormalTok{]}
\CommentTok{\#>  [1] "Oregon State Ichthyology Collection"                                                                                                                                                  }
\CommentTok{\#>  [2] "Oregon State University Herpetological Collection"                                                                                                                                    }
\CommentTok{\#>  [3] "Mygalomorph spiders from southwestern Oregon, USA, with descriptions of four new species"                                                                                             }
\CommentTok{\#>  [4] "A new species of Helobdella (Hirudinida: Glossiphoniidae) from Oregon, USA"                                                                                                           }
\CommentTok{\#>  [5] "Cave millipedes of the United States. XVI. Two new species from Oregon Caves National Monument, Oregon (Chordeumatida, Conotylidae and Caseyidae)"                                    }
\CommentTok{\#>  [6] "Annotated Checklist of the large branchiopod crustaceans of Idaho, Oregon and Washington, USA, with the “ rediscovery ” of a new species of Branchinecta (Anostraca: Branchinectidae)"}
\CommentTok{\#>  [7] "A new species of Chrysobothris Eschscholtz from Oregon and Washington, with notes on other Buprestidae (Coleoptera) occurring in the United States and Canada"                        }
\CommentTok{\#>  [8] "Three new species of Grylloblatta Walker (Insecta: Grylloblattodea: Grylloblattidae), from southern Oregon and northern California"                                                   }
\CommentTok{\#>  [9] "A new species of Cladotanytarsus (Lenziella) from Oregon supports the systematic concept of the subgenus (Diptera: Chironomidae)"                                                     }
\CommentTok{\#> [10] "Two new species of Fluminicola (Caenogastropoda, Lithoglyphidae) from southwest Oregon, USA, and a range extension for F. multifarius"}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{require }\StringTok{\textquotesingle{}gbifrb\textquotesingle{}}
\NormalTok{registry = }\DataTypeTok{Gbif}\NormalTok{::}\DataTypeTok{Registry}
\NormalTok{registry.datasets(}\StringTok{type: "OCCURRENCE"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{dataset-metrics}{%
\subsection{Dataset metrics}\label{dataset-metrics}}

Dataset metrics are another useful way of figuring out what datasets you
may want to use. One drawback is that these metrics data are only
available for datasets of type \emph{checklist}, but there are quite a
lot of them (29853).

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res <{-}}\StringTok{ }\KeywordTok{dataset\_metrics}\NormalTok{(}\DataTypeTok{uuid=}\StringTok{\textquotesingle{}ec93a739{-}1681{-}4b04{-}b62f{-}3a687127a17f\textquotesingle{}}\NormalTok{)}
\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{rank =} \KeywordTok{names}\NormalTok{(res}\OperatorTok{$}\NormalTok{countByRank),}
           \DataTypeTok{count =} \KeywordTok{unname}\NormalTok{(}\KeywordTok{unlist}\NormalTok{(res}\OperatorTok{$}\NormalTok{countByRank)))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ pygbif }\ImportTok{import}\NormalTok{ registry}
\NormalTok{registry.dataset\_metrics(uuid}\OperatorTok{=}\StringTok{\textquotesingle{}ec93a739{-}1681{-}4b04{-}b62f{-}3a687127a17f\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{require }\StringTok{\textquotesingle{}gbifrb\textquotesingle{}}
\NormalTok{registry = }\DataTypeTok{Gbif}\NormalTok{::}\DataTypeTok{Registry}
\NormalTok{registry.dataset\_metrics(}\StringTok{uuid: \textquotesingle{}ec93a739{-}1681{-}4b04{-}b62f{-}3a687127a17f\textquotesingle{}}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{networks-nodes-and-installations}{%
\subsection{Networks, nodes, and
installations}\label{networks-nodes-and-installations}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{networks}\NormalTok{(}\DataTypeTok{limit =} \DecValTok{10}\NormalTok{)}\OperatorTok{$}\NormalTok{data}\OperatorTok{$}\NormalTok{title}
\CommentTok{\#> [1] "TrIAS"                                        }
\CommentTok{\#> [2] "Arctos"                                       }
\CommentTok{\#> [3] "Freshwater Network"                           }
\CommentTok{\#> [4] "Ocean Biogeographic Information System (OBIS)"}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{require }\StringTok{\textquotesingle{}gbifrb\textquotesingle{}}
\NormalTok{registry = }\DataTypeTok{Gbif}\NormalTok{::}\DataTypeTok{Registry}
\NormalTok{registry.networks(}\StringTok{limit: }\DecValTok{10}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{taxonomic-names}{%
\subsection{Taxonomic names}\label{taxonomic-names}}

@@

\hypertarget{gbif-backbone}{%
\subsection{GBIF Backbone}\label{gbif-backbone}}

The GBIF backbone taxonomy is used in GBIF to have a consistent way to
refer to taxonomic names throughout their services. The backbone has
6575748 unique names and 2730631 species names. The backbone taxonomy is
also a dataset with key \texttt{d7dddbf4-2cf0-4f39-9b2a-bb099caae36c}
(\url{https://www.gbif.org/dataset/d7dddbf4-2cf0-4f39-9b2a-bb099caae36c}).

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{res <{-}}\StringTok{ }\KeywordTok{name\_backbone}\NormalTok{(}\DataTypeTok{name=}\StringTok{\textquotesingle{}Poa\textquotesingle{}}\NormalTok{, }\DataTypeTok{rank=}\StringTok{\textquotesingle{}genus\textquotesingle{}}\NormalTok{, }\DataTypeTok{family=}\StringTok{\textquotesingle{}Poaceae\textquotesingle{}}\NormalTok{)}
\NormalTok{res[}\KeywordTok{c}\NormalTok{(}\StringTok{\textquotesingle{}usageKey\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}kingdom\textquotesingle{}}\NormalTok{)]}
\CommentTok{\#> \# A tibble: 1 x 2}
\CommentTok{\#>   usageKey kingdom}
\CommentTok{\#>      <int> <chr>  }
\CommentTok{\#> 1  2704173 Plantae}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ pygbif }\ImportTok{import}\NormalTok{ species}
\NormalTok{res }\OperatorTok{=}\NormalTok{ species.name\_backbone(name}\OperatorTok{=}\StringTok{\textquotesingle{}Poa\textquotesingle{}}\NormalTok{, rank}\OperatorTok{=}\StringTok{\textquotesingle{}genus\textquotesingle{}}\NormalTok{, family}\OperatorTok{=}\StringTok{\textquotesingle{}Poaceae\textquotesingle{}}\NormalTok{)}
\NormalTok{[ res[x] }\ControlFlowTok{for}\NormalTok{ x }\KeywordTok{in}\NormalTok{ [}\StringTok{\textquotesingle{}usageKey\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}kingdom\textquotesingle{}}\NormalTok{] ]}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{require }\StringTok{\textquotesingle{}gbifrb\textquotesingle{}}
\NormalTok{species = }\DataTypeTok{Gbif}\NormalTok{::}\DataTypeTok{Species}
\NormalTok{res = species.name\_backbone(}\StringTok{name: \textquotesingle{}Poa\textquotesingle{}}\NormalTok{, }\StringTok{rank: \textquotesingle{}genus\textquotesingle{}}\NormalTok{, }\StringTok{family: \textquotesingle{}Poaceae\textquotesingle{}}\NormalTok{)}
\NormalTok{res.select \{ |k,v| k.match(}\OtherTok{/usageKey|kingdom/}\NormalTok{) \}}
\end{Highlighting}
\end{Shaded}

\hypertarget{name-searching}{%
\subsection{Name searching}\label{name-searching}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{name\_suggest}\NormalTok{(}\DataTypeTok{q=}\StringTok{\textquotesingle{}Pum\textquotesingle{}}\NormalTok{, }\DataTypeTok{limit =} \DecValTok{6}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}rll@{}}
\toprule
key & canonicalName & rank\tabularnewline
\midrule
\endhead
2142856 & Althepus pum & SPECIES\tabularnewline
8589398 & Pumiliopimoidae & FAMILY\tabularnewline
8608394 & Pumiliopimoa & GENUS\tabularnewline
4579844 & Pumilibaxa & GENUS\tabularnewline
4581745 & Pumicia & GENUS\tabularnewline
8783253 & Pumililema & GENUS\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ pygbif }\ImportTok{import}\NormalTok{ species}
\NormalTok{species.name\_suggest(q}\OperatorTok{=}\StringTok{\textquotesingle{}Pum\textquotesingle{}}\NormalTok{, limit }\OperatorTok{=} \DecValTok{6}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{require }\StringTok{\textquotesingle{}gbifrb\textquotesingle{}}
\NormalTok{species = }\DataTypeTok{Gbif}\NormalTok{::}\DataTypeTok{Species}
\NormalTok{species.name\_suggest(}\StringTok{q: \textquotesingle{}Pum\textquotesingle{}}\NormalTok{, }\StringTok{limit: }\DecValTok{6}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\hypertarget{occurrences}{%
\subsection{Occurrences}\label{occurrences}}

@@

\hypertarget{occurrences-download-api}{%
\subsection{Occurrences Download API}\label{occurrences-download-api}}

@@

Request data download given a query. Here, we search for the taxon key
\texttt{3119195}, which is the key for \emph{Helianthus annuus}
(http://www.gbif.org/species/3119195).

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{occ\_download}\NormalTok{(}\StringTok{\textquotesingle{}taxonKey = 3119195\textquotesingle{}}\NormalTok{)}
\CommentTok{\#> <<gbif download>>}
\CommentTok{\#>   Username: xxxx}
\CommentTok{\#>   E{-}mail: xxxx}
\CommentTok{\#>   Download key: 0000840{-}150615163101818}
\end{Highlighting}
\end{Shaded}
